Material Metohds

### 2019-09-17 doc/MatMeth.Rmd
barfed more text for mat and meth. needs cleaning up

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_MatMeth.bib
---

@@

From males, the right teste was collected and processed. (Ages are listed in supplmental material). Ovaries were collected from neonates less than 48 hours old or embryos between e16 to 21.

The behavior of these strains did not allow us to check for copulary plugs, resulting in most oocyte data coming from neonate mice between 5 to 48 hours.

@@

After incubation, gonads were transferred to sucrose solution -for mastication to make a cell slurry which was transferred to 80ul of 2% PFA solution. Cells were fixed in this solution and dried in a humid chamber at room temperature overnight. The next morning, slides were treated with a photoflow wash.

@@

For MLH1 pachytene characterization, Cells with a full karyotype (19 autosomes and XY for spermatocyte spreads or 20 bivalents for oocyte spreads), distinct foci, and intact bivalents were included for quantification.

Reprocessing in Photoshop ()- Image file names were anonymized before manual scoring of MLH1 or DMC1 foci.

@@

-done in R/ specific packages
-non-parameteric  (tests and measures for dealing with count data)

-hypothese tested (size, DSB number)

>>>>

---
title: "Material Metohds"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_MatMeth.bib
---

@@

From males, the right teste was collected and processed as discribed in X citation. The majority of mice used were betwee 5 and 12 weeks, (supplemental table). However some strains had problems breeding, so testes from older mice were collected. We found a (small/no) age effect on MLH1 counts for male mice (Supplemental Figure)).

The vast majority of oocyte data was collected from neonate litters/mice between 5 to 48 hours. This approach maintain breeding pairing and still result in prophase oocytes (cite timeline of oocytes in neonates). (differences were assessed between embryo samples and neonates?). Presice staging of embryos by checking copulary plugs was diffcult/not feasible in many of these wild derived strains due to their behavior. Embryonic samples were collected when pregenacgy noted in females, embryos were staged based on (X table markers).

@@

After incubation, gonads were transferred to sucrose solution -for mastication to make a cell slurry which was transferred to 80ul of 2% PFA solution. Cells were fixed in this solution and dried in a humid chamber at room temperature overnight. The next morning, slides were treated with a photoflow (Kodak, cite) wash.

Staining / Immunohistochemistry

The same staining protocol was applied to spermatocyte and oocyte spreads.
The staining protocol was bas on X with some adaptations, and same as previously discribed in Peterson etal 2019.

@@

Images of cells were capture on Axio-2 microscope.

For MLH1 pachytene characterization, Cells with a full karyotype (19 acrocentric bivalents and XY for spermatocytes or 20 acrocentric bivalents for oocytes), distinct foci, and intact bivalents were included for quantification.
Reprocessing in Photoshop (cite). Image file names were anonymized before manual scoring of MLH1 or DMC1 foci.

Hand measures dataset generated by using ImageJ.

total Sc was measured (Rwang et al 2019)

Bivalent level measure were done (Peterson et al 2019)

@@

Statistical analysis was performed in R (version and cite).

The distributions of CO counts per cell was assessed for normailty (supplemental figure). Mouse mean MLH1 count was used to get around the bad discreet nature of count data. (normality was confirmed with X distrbution, supplememtal figure).

-specific statistical tests; (means, non-parameteric kurts wallis t-test?) (correlation coeffectent (function))
linear models lm() from X package.

-specific R packages
-non-parameteric  (tests and measures for dealing with count data)
-hypothese tested (size, DSB number)

Comparison/analysis of variation in MLH1 counts within and between groups was done within a general linear/ mixmodel frame work, using X package (cite).
With X formula Co count ~ blah + blah, with random strain specific sex effect.

(we used this frame work as proxy for 'polymorphism' and 'divergence' in MLH1 counts across house mouse and closeley related species.)
